Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/conclusion.tex
ran out of gas for a soaring finish

\section{Conclusion}
% Chokepoint Potential
In this paper we have introduced two novel measures, chokepoint potential, on single border ASes,
and national breakthrough potential, on entire nations, that together allow us to
evaluate the level of difficulty that a government faces when trying to censor the Internet
based entirely on AS-level topology. Our technique for evaluating AS-level topology using
\toolname{} provides a monitoring capability of BGP dynamics that was previously not possible.
We have taken advantage of efficient simulation, standard AS relationship datasets, and cross-platform
design principles so that this tool is readily deployable for future research.
% Ecolution over time
\par
Our application of \toolname{} to investigate evolution of the global AS graph over time shows us
interesting trends in AS topologies. We have identified the apparent lack of major nations to develop
more open Internet borders and gateways, despite the increasing connectivity and size of the AS graph. Additionally,
we find that the chokepoints in some nations known to conduct censorship and surveillance have increased in strength.
% Internet Freedom
\par
We have validated national breakthrough potential as having a relationship to actual censorship by showing
the significance of the relationship between the chokepoint potential of nations and the evaluations of freedom provided
by both freedom on the net and freedom of the press. This relationship implies that when censorship and surveillance are being evaluated
at the national level, it is worthwhile to consider the border AS chokepoints that are resident to the nation in question.

>>>>

\section{Conclusion}
% Chokepoint Potential
This paper addresses the question of how Internet structure relates to 
international boundaries and how it is changing over time.  By defining chokepoint
potential, both for individual border ASes and aggregated by country,
we provide a quantitative way to measure these effects in terms of the ease
with which a government can control routing paths across its borders. 
Our technique for generating BGP paths and evaluating chokepoints
using \toolname{} provides public domain software and routing trees for the entire AS graph.
%a monitoring capability of BGP dynamics that was previously not possible.
We have taken advantage of efficient simulation, standard AS relationship datasets, and cross-platform
design principles so that this tool will be readily deployable for future research.
% Ecolution over time
\par We used \toolname{} to investigate how the global AS graph has
evolved over time, finding interesting trends and outliers. These
studies reveal a tendency in large nations to concentrate paths across
their borders into a small number of ASes, despite the increasing
connectivity and size of the AS graph. Additionally, we find that border
chokepoints in some nations known to conduct censorship and
surveillance have steadily increased in strength.
% Internet Freedom
\par
We studied the relationship between NCP and two evaluations of openness, Freedom of the Net  and Freedom of the press, finding stastistically significant relationships in both cases.
%These results suggest that it is worthwhile to consider border AS chokepoints when studying
This relationship implies that when censorship and surveillance are
being evaluated at the national level, it is worthwhile to consider
the border AS chokepoints that are resident to the nation in question.
